### 2015-06-21 stochastic/stochastic-recovery.Rmd
stochastic recovery

```{r}
set.seed(1)
n_spp = 250
n_loc = 2500
n_env = 3
n_gibbs = 1000

@@

  # Calculate the gradient with respect to alpha and beta
  delta_stats = y_stats - y_sim_stats
  beta_grad = (delta_stats - 10 * beta) / 10 / n_loc # Subtract beta as weight decay

@@

```{r}
pdf("poster-alpha.pdf", width = 4, height = 5)
plot(alpha_env, true_alpha_env,
     pch = 16, cex = .4, col = "#00000090",
     xlab = "Estimated environmental coefficient",
     ylab = "\"True\" environmental coefficient",
     main = paste0("Recoverd environmental coefficients", "\nN = ", length(alpha_env)),
     las = 1,
     cex.axis = 0.75
)
text(
  -1, 
  1,
  paste(
    "R^2 =", 
    signif(cor(c(alpha_env), c(true_alpha_env))^2, 2)
  )
)
dev.off()

```

>>>>

```{r}
set.seed(1)
n_spp = 100
n_loc = 1000
n_env = 3
n_gibbs = 1000

@@

  # Calculate the gradient with respect to alpha and beta
  delta_stats = y_stats - y_sim_stats
  beta_grad = (delta_stats - beta) / 10 / n_loc # Subtract beta as weight decay

@@

```{r}
pdf("poster-alpha.pdf", width = 4, height = 5)
plot(alpha_env, true_alpha_env,
     pch = 16, cex = .4, col = "#00000090",
     xlab = "Estimated environmental coefficient",
     ylab = "\"True\" environmental coefficient",
     main = paste0("Recoverd environmental coefficients", "\nN = ", length(alpha_env)),
     las = 1,
     cex.axis = 0.75
)
text(
  -1, 
  1,
  paste(
    "R^2 =", 
    signif(cor(c(alpha_env), c(true_alpha_env))^2, 2)
  )
)
dev.off()
```
